\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
% \usepackage{cite}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{cite}
    
\begin{document}

\title{Isaac's Tournament: A Comparison of The State of the Art in Multi-Robot Pursuit-Evasion Games}

\author{
    \IEEEauthorblockN{Luka Antonyshyn, Anthony Beca, Aoran Jiao, and Elliot Preston-Krebs}
    \IEEEauthorblockA{\textit{Institute for Aerospace Studies, University of Toronto}, Toronto, Canada \\
    \{luka.antonyshyn, anthony.beca, aoran.jiao, elliot.prestonkrebs\}@robotics.utias.utoronto.ca}
}

\maketitle

\begin{abstract}
	The study of planning under adversarial conditions has become of great interest as the adoption of robotics for security, defense, and surveillance increases. 
	Further, adversarial planning can be used to account for worst-case scenarios in critical areas, such as risk-aware motion planning or search and rescue.
	Often, this study is conducted under the framework of differential game theory, a methodology that studies optimal outcomes of scenarios with multiple rational actors that evolve according to differential equations.
    One such scenario is the $N$-pursuer visibility-based pursuit evasion game, in which a team of pursuers attempts to examine an entire area in such a way that a moving evader would be unable to escape detection.
	This game has been used to model environmental inspection, perimeter defense, and search and rescue problems, but most approaches tend to only evaluate on simple scenarios and against similar approaches.
	In this report, we rectify this gap through the study and comparison the quantitative and qualitative results associated with several state of the art approaches.
\end{abstract}

\begin{IEEEkeywords}
\end{IEEEkeywords}

\section{Introduction}
% give a high level overview of your project - is it a technique, or the application of a specific algorithm, etc.? Who (worldwide) the major players in the area? Why is the topic interesting?
Adversarial games in continuous spaces have long been studied under the field of differential game theory, developed by Rufus Isaac's in the 1960s~\cite{diff_games}.
These games, contrary to their discrete classical game theoretical counterpoints, have the evolution of the game evolve according to differential equations.
Differential games have been used in several application spaces, such as perimeter defense, risk-averse landing path planning for airplanes, and search and rescue~\cite{pursuit}.

Recently, more interest has been taken in multi-agent differential games. 
These, of course, model more realistic scenarios and engagements. 
However, they must often settle for sub-optimal solutions due to the curse of dimensionality and the difficulty of computing Hamilton-Jacobi-Isaacs solutions~\cite{multi_diff}.
As a result, much work has been focussed on the development of heuristics, learning-based approaches, and approximate solutions.

One such multi-agent game is the multi-pursuer vision-based pursuit evasion game.
In this formulation, the evader, or evaders, are often treated as abstract entities that can move at arbitrary speeds. 
This forces the pursuing team to plan for the worst-case scenario.
As such, the problem devolves into a type of constrained frontier expansion problem on a known path.
This makes the formulation of interest to motion planning researchers.
 
Many solutions have been proposed for this problem, from learning-based methods~\cite{}, sampling-based approaches\cite{}, and graph-search algorithms~\cite{}.
However, in the literature, practitioners tend to compare only against solutions they have readily available - ignoring suitable baselines from other problem formulations and only evaluating on limited subsets of the total problem space.
As such, the state of the art is lacking in honest analysis and comparison of different approaches to multi-agent differential games.

Following the growth of popularity of game theory, an effort to evaluate the performance of different strategies was undertaken on Axelrod's tournament - a contest in which different policies were pitted against each other in varying conditions to compare outcomes.
Here, we pursue a simplified version of Axelrod's tournament on one differential game.
We implement four approaches to the multi-pursuer observability-based pursuit evasion game, and compare them on numerous scenarios using common metrics.
We identify and analyse the behaviours of each method under various conditions that challenge their formulations, and use the information to recommend steps for future works.

The remainder of this work is organized as follows; in Section \ref{sec:lit_rev}, we review the related works; in Section \ref{sec:background}, we state the exact problem formulation; in Section \ref{sec:algo}, we detail the individual algorithms we implement and evaluate, in Section \ref{}, we detail our methodology for comparison; in Section \ref{sec:comp}, we discuss and analyse the methods comparisons and failure modes; and in Section \ref{sec:open_prob}, we identify promising areas for further investigatin.

\section{Background} \label{sec:background}

\subsection{Pursuit-Evasion Games}

Pursuit-evasion games study the interaction between one or more pursuers and one or more evaders moving in a domain $\mathcal{D} \subset \mathbb{R}^d$. 
The objective of the pursuers is to capture the evaders, while the evaders aim to avoid capture. 
These problems arise in robotics, control theory, and differential games.

A common formulation models the players as dynamical systems. 
For a single pursuer with state $x_p(t)$ and evader with state $x_e(t)$, their dynamics may be written as
\[
\dot{x}_p(t) = u_p(t), \quad \dot{x}_e(t) = u_e(t),
\]
where $u_p(t), u_e(t) \in \mathcal{U}$ are control inputs subject to bounded speed constraints, e.g., $\|u_p\| \leq v_p$, $\|u_e\| \leq v_e$. The game terminates upon capture, often defined as
\[
\|x_p(t) - x_e(t)\| \leq \varepsilon,
\]
for some radius $\varepsilon > 0$.

The pursuer seeks a control strategy $u_p(\cdot)$ that guarantees capture in finite time, while the evader seeks to maximize the capture time or avoid capture indefinitely. 
Strategies may be open-loop or feedback, and optimal strategies are often characterized using tools from differential game theory, such as Hamilton-Jacobi-Isaacs (HJI) equations~\cite{diff_games}.
In higher dimensional spaces, ore even with more complex kinematics, solutions to these equations are often intractable to compute.

\subsection{The N-Pursuer Visibility-Based Pursuit-Evasion Game}

In the N-pursuer visibility-based pursuit-evasion problem, a team of $N$ pursuers cooperatively searches for an evader with an unknown position in a known environment $\mathcal{D} \subset \mathbb{R}^2$.
We denote the configuration space of the environment, exclusive of obstacles, as $\mathcal{C} \subset \mathcal{D}$.
One key distinction from the standard model of the pursuit-evasion game is that information is limited by line-of-sight visibility: the evader is detected only if it lies within the visible region of at least one pursuer.
This visible region is defined by the joint configurations of the pursuer, the shape of $\mathcal{C}$, and the position of obstacles~\cite{vis_pursuit}.

Let the pursuers have states $\{x_i(t)\}_{i=1}^N \subset \mathcal{C}$. The environment induces a visibility map: for a pursuer at $x_i$, its visibility region is
\[
\mathcal{V}(x_i) = \{ y \in \mathcal{D} \mid \text{$y$ is visible from $x_i$} \}.
\]
In this variation of the pursuit evasion-game, the evader is often treated as an abstraction rather than a physical entity. 
We assume the position of the pursuer $e(t) \in \mathcal{C}$ at time $t$ is a continuous function $e:[0,\infty) \to\mathcal{C}$ that describes the path of the evader moving at arbitrary speeds. 
This allows the evader to inhabit any location in a connected subspace $\mathcal{S}\in \mathcal{C}\\ \mathcal{V}(x)$. We refer to $\mathcal{S}(t)$ as the shadow set at time $t$. 

Unlike classical pursuit-evasion, the goal is not immediate capture of the evader but guaranteed detection. 
The pursuers seek strategies that ensure that, regardless of the evader trajectory, the evader will eventually be observed:
\[
\exists\, T < \infty \ \text{such that} \ e(T) \in \bigcup_{i=1}^N \mathcal{V}(x_i(T)).
\]

A central concept is the partition of $\mathcal{C}$ into cleared and contaminated regions. 
A point $y \in \mathcal{C}$ is cleared at time $t$ if it has been visible to some pursuer at some prior time and cannot be re-entered by the evader without being detected. 
This is equivalent to it not being path-connected to a contaminated region.
Otherwise, the point is contaminated.
Let $\mathcal{\tilde{S}}(t)$ and $\mathcal{\bar{S}}(t)$ denote the cleared and contaminated regions, respectively, with
\[
\mathcal{C} = \mathcal{\tilde{S}}(t) \cup \mathcal{\bar{S}}(t).
\]
Pursuer strategies must ensure that $\mathcal{\bar{S}}(t)$ shrinks monotonically, avoiding recontamination.
This effectively collapses to a constrained form of the frontier expansion problem, where frontiers are dynamic and may rejoin each other.

The visibility-based pursuit-evasion problem is significantly harder than classical pursuit-evasion due to partial information and the need for coordination. 
Determining the minimum $N$ required for guaranteed detection is generally NP-hard~\cite{vis_pursuit}. 
This leads to many discretizations, sampling-based methods and learning approaches to the problem.

\subsection{Shadow Events}
Central to some algorithms in the literature is the concept of shadow events. 
This framework provides a conceptual analog of pursuer movement that neatly fits into the N-Pursuer Visibility-Based Pursuit-Evasion game.
Briefly, shadow events describe a framework for propagating labels assigned to particular unseen regions in a space based on a hierarchy of dominance under common interactons.

Introduced in \cite{guibas1999visibility}, shadow events are primarily used to keep track of contaminated areas in the game's space of interest.
As such, the labels of concern are whether an area is clear or contaminated.
Naturally, contaminated labels dominate cleared labels, as when a shadow we have cleared intersects with an unchecked shadow, the evading agent may move into the previously check space.

Five main shadow events are introduced. These are
\begin{itemize}
	\item Appear - A shadow is instantiated when a prviously seen part of the environment becomes hidden.
	\item Disappear - Existing shadows vanish when the come into the visibility cone of the pursuers.
	\item Merge - Two or more existing shadows join together and adopt the same shadow label when a shadow appears linking them together.
	\item Split - One shadow can be divided into multiple shadows when the pursuers visibility cones cause them to be non-path connected in 4-neighbour space.
\end{itemize}
In practice these events are calculated on a continuous space by discretizing into a grid, calculating shadows based on line of sight from agent positions in a joint configurations, and propagating dominant labels to the 4-neighbours of any unseen cell. 

Before desribing the process of propogating labels, we begin with the following definition. 
A shadow is clear at a time $t$ if it is not possible for an evader, as defined earlier, to inhabit the shadow. 
Otherwise, a shadow is contaminated.

We may now state the relationship between the shadow events and labels as
\begin{itemize}
	\item Appear - A shadow appearing from previously visible areas is marked clear.
	\item Disappear - Labels are discarded
	\item Merge - When shadows merge, the dominant label is assigned to all of the shadows. That is to say, if any of the merging shadows is contaminated,the resulting shadow is contaminated, and otherwise it is clear.
	\item Split - All shadows resulting from a split inherit the label of the original shadow.
\end{itemize}

Of course, algorithms may use this information in their planning loop, and several considered implementations do so~\cite{stiffler2014sampling}.
The primary drawback of this approach is the extreme cost of computing the shadow label propagation. 
in a 64mx64m environment at a resolution of 1m, discretization yields 4096 cells, each of which has to be check for line of sight from $N$ positions.
Every resulting shadow position then must be checked for neighbours, resulting in a breadth first search through the graph for all connected shadows.
This leads to significant slow-downs in sampling on more complex and larger maps.
Speed-ups can be made by decreasing the resolution, but this comes at the cost of potentially missing contaminations.

Nonetheless, this concept provides a simple way to monitor and evaluate approaches to this problem.
As such we find it useful to utilize shadow labels as a metric in the evaluation of the various algorithms detailed below.


\subsection{Sampling-Based Motion Planning}
The Probabilistic Roadmap (PRM) is a sampling-based motion planning algorithm designed for multi-query scenarios in high-dimensional configuration spaces~\cite{kavraki1996probabilistic}. 
PRM constructs an undirected graph (roadmap) $G = (V, E)$ that approximates the connectivity of $\mathcal{C}_{\mathrm{free}}$. The algorithm proceeds in two phases:

During the initial sampling phase, a set of $n$ configurations $\{q_1, \dots, q_n\}$ is sampled independently from $\mathcal{C}_{\mathrm{free}}$, typically using a uniform distribution:
\[
q_i \sim \mathrm{Unif}(\mathcal{C}_{\mathrm{free}}).
\]
Each valid sample becomes a vertex in $V$. For each $q_i$, a set of neighboring vertices is selected using a metric $\rho(\cdot,\cdot)$ (e.g., $k$-nearest neighbors or within radius $r_n$). For each neighbor $q_j$, a local planner attempts to connect $q_i$ and $q_j$ by a simple path:
\[
\sigma_{ij}(t) = (1 - t) q_i + t q_j, \quad t \in [0,1].
\]
An edge $(q_i, q_j) \in E$ is added if $\sigma_{ij}(t) \subset \mathcal{C}_{\mathrm{free}}$.

In the query phase, given start and goal configurations $q_{\mathrm{start}}, q_{\mathrm{goal}} \in \mathcal{C}$, are connected to nearby vertices in $G$ using the local planner. 
A graph search algorithm is then used to find a path in $G$.

PRM is probabilistically complete: if a path exists in $\mathcal{C}_{\mathrm{free}}$, the probability that PRM finds a solution approaches $1$ as $n \to \infty$.
Under appropriate connection strategies (e.g., $r_n \sim (\log n / n)^{1/d}$ in $d$ dimensions), PRM variants can achieve asymptotic optimality, and have been applied to numerous multi-robot problems~\cite{CLARK2005244}.



\subsection{Graph-Based Motion Planning}

Graph-based motion planning transforms the continuous $C$-space into a discrete topological representation $G = (V,E)$. In this formulation, vertices $v \in V$ represent discrete configurations in $C_{free}$, while edges $e \in E$ represent feasible transitions between them. The framework typically follows a three step pipeline: a discretization phase, followed by edge weight aChosetssignment based on cost metrics, and a graph search algorithm to extract a least-cost path.

The literature offers diverse approaches. Discretization may utlize exact cell decompositions (i.e. visibility graphs, Morse cells, or convex partitions \cite{choset2005principles}), or approximate grid-based decompositions. While classic methods like Breadth-First-Search (BFS) or Depth-First-Search (DFS) provide basic connectivity, modern motion planning heavily leverages informed search heurstics (namely A*) to manage the computational complexity inherent in high-dimensional state spaces.

\subsection{Multi-Agent Reinforcement Learning}

Reinforcement learning~(RL) studies sequential decision-making problems in which an agent selects actions from observations and updates its policy using scalar rewards.
In the standard Markov decision process~(MDP) formulation, a policy $\pi_\theta(a_t\mid s_t)$ is trained to maximize expected return,
\[
J(\theta)=\mathbb{E}_{\pi_\theta}\left[\sum_{t=0}^{T}\gamma^t r_t\right].
\]
Robotic pursuit-evasion is usually only partially observable, so the policy is often conditioned on local observations $o_t$, partial maps, or observation histories rather than the true full state.

Multi-agent reinforcement learning~(MARL) generalizes this setting to $N$ decision-making agents.
Each agent $i$ receives an observation $o_i(t)$, chooses an action $a_i(t)$, and the joint action $a(t)=(a_1(t),\ldots,a_N(t))$ determines the next state and team reward.
In cooperative games, the agents may share a common reward, but the policy must still determine which individual actions contributed to the team-level outcome.
This is the credit assignment problem.
Independent learning also makes the environment non-stationary from the perspective of any one agent, since the other agents' policies change during training.

A common way to address this issue is centralized training with decentralized execution~(CTDE).
During training, a critic or value estimator may use additional information such as the full team state, while execution is performed by decentralized policies.
Actor-critic algorithms are a common implementation of this idea: the actor represents the policy, while the critic estimates the value of states or state-action pairs and guides the policy update.
Off-policy methods reuse stored experience, while on-policy methods update from recently collected trajectories.
For spatial multi-agent problems, learned policies are often paired with graph neural networks or attention layers so that variable-size maps and teams can be encoded without flattening everything into a fixed-size vector.

\section{Literature Review}\label{sec:lit_rev}
% Provide a structured review of seminal and recent work in your topic area. You should attemp to provide a (brief) taxonomy of research results, organized in such a way that someone reading your report will be able ot understand some common research threads
The pursuit-evasion game was originally introduced by Rufus Isaacs in his seminal work on differential game theory~\cite{diff_games}.
Isaacs detailed a method for finding optimal solutions to differential games, relying on an equation, dubbed the Hamilton-Jacobi-Isaacs~(HJI) equation.
The solution to this equation is tractable to calculate analytically in low-dimensional spaces.
Below, we provide an overview of several approaches to the N-pursuer visibility-based pursuit-evasion game. 

\subsection{Sampling-based Approaches}

Sampling-based motion planning methods have long been studied for their ability to find high-quality solutions to challenging configuration spaces in reasonable amounts of time~\cite{FMT}.
Common sampling-based methods include the randomly-exploring rapid tree algorithms~\cite{lavalle98rrt}, the fast marching tree algorithm~\cite{FMT}, and the probabilistic road-map~(PRM) algorithm~\cite{kavraki1996probabilistic}.
Unfortunately, these algorithms tend to struggle in joint configuration spaces as a result of the curse of dimensionality, leading to several multi-robot variations~\cite{CLARK2005244}.

Due to the high dimensional nature of the joint configuration space, sampling-based approaches to the problem are fairly common.
In one such method, Stifler and O'Kane propose a PRM-style planner that utilizes an internal model of the evolution of visible spaces as an additional validity check on expanding nodes during planning~\cite{}.
In a follow up work, the algorithm preformance is improved through the use of domain-specific pose sampling, and a solution-refinement method~\cite{}.
Several additional extensions to this method have been considered, including the improvement robustness to individual robot failures~\cite{} and the imposition of more stringent robot sensing models~\cite{}.




\subsection{Graph-based Approaches}

Guibas and Lavalle \cite{guibas1997visibility} formalized the pursuit-evasion problem in continuous polygonal environments with recontaminations. They develop a complete algorithm for the case of a single pursuer. First, the workspace is partititioned into convex regions, with binary labels indicating contamination, then a search is performed on the resulting quotient information space. By the definition of convexity, all points in a convex cell are mutually visible \cite{boyd2004convex}, therefore, the pursuer's progress is tracked by its transitions between these cells. The distance between centroids as well as the contamination state are used as an information-based heuristic for Dijkstra's algorithm. They show a logarithmic bound on the number of needed pursuers (i.e. the search number) for simply-connected free spaces, but leave multi-agent algorithms for future work. As part of this work, we implemented the Guibas algorithm for a single pursuer.

The most relevant paper for our tournament (respecting all game constraints) proposes Graph-Clear \cite{kolling2009pursuit}. A team of robots can execute \textit{sweep} actions to detect evaders in a vertex, and \textit{block} actions to prevent intruders from crossing an edge. A strategy consists of a sequence of block and sweep actions to detect all intruders despite possible recontamination. They show the computation of optimal strategies for this game is NP-hard for graphs; therefore the authors propose to create spanning trees, for which a Graph-Clear is a polynomial time algorithm. Intuitively, cycles in the graph are broken by agents executing a block action, reducing the problem to a tree search to be executed by the remaining agents.

Some recent works tackle similar problem formulations, but do not qualify for the restrictions of this comparison. Namely, Zhou \cite{zhou2016cooperative} and Huang \cite{huang2011guaranteed} separately develop decentralized strategies for multiple pursuers in planar environments based on Voronoi decompositions; but evaders have finite speed. Bhattacharya et. al \cite{BHATTACHARYA20101745} analyze a cops and robber game in multidimensional grids, but cops are able to ``teleport'' across cells.

\subsection{Learning-based Approaches}

Learning-based approaches to pursuit-evasion can be separated into two broad groups.
The first considers pursuit as a chasing or interception problem, where the evader's state is available to the pursuers.
For example, decentralized deep RL has been used to train multiple pursuers under local sensing and communication constraints~\cite{de2021decentralized}.
These methods are relevant for multi-agent coordination, but they do not address the clearing problem considered here because the evader is localized and has bounded dynamics.

The second group uses learning as a substitute for explicit search over the information space.
Rather than enumerating all possible contamination labels, a policy learns useful clearing and guarding behavior from simulation.
This can scale better at execution time, but it trades away the completeness guarantees associated with graph-search methods.

ViPER~(Visibility-based Pursuit-Evasion via Reinforcement Learning) is the most directly relevant learning-based approach for this report~\cite{wang2024viper}.
It is designed specifically for visibility-based clearing with omniscient, potentially arbitrarily fast evaders.
ViPER builds a graph of candidate viewpoints over the known free space, augments each node with frontier and clearing information, and uses graph attention to learn which neighboring viewpoint each agent should visit next.
The method follows CTDE, similar in spirit to multi-agent actor-critic methods such as MADDPG~\cite{lowe2017multiagent}: the deployed policy is decentralized, while the training critic uses privileged map and team-action information.
ViPER also uses an attentive critic, similar in motivation to MAAC~\cite{iqbal2019actor}, to improve credit assignment.
Its main limitation is that it does not certify clearing in the same way as complete planners; success must be measured by the simulator or an external contamination tracker.


\section{Algorithm Implementation}\label{sec:algo}
% What did you implement, and what were the results you obtained? What information is presented in the tables, figures, and diagrams you have included? This is the 'meat' of the report - when writing this section, step back and consider how best to convey your results to someone who is new to the topic.
As we are interested in comparing recent developments in the field, we sampled and implemented 4 algorithms, one from each problem formulation.
These are then compared on common metrics using a series of different maps.
Below, we detail every algorithm selected for comparison.

\subsection{Sample-Generated Pursuit-Evasion Graphs}
Sample-generated pursuit-evasion graphs~(SG-PEG) utilize RRT-style sampling in a joint configuration space to find solutions to the VB-PE game.
While based on RRT algorihtms, no proofs of probabilistic completeness are provided for SG-PEG.

We begin with a description of the graph data structure utilized in SG-PEG.
The graph utilizes is a rooted di-graph with vertices representing joint robot configurations $r_{0:N}$, as well as the set of non-dominated shadows reachable by traversing the graph to the vertex in question.
For an edge to be considered valid in the context of the graph, a line in the joint configuration space $\mathcal{C}^N$ must exist that maps reachable configurations of shadow labels at the source vertex to the same at the target vertex.

The core complexity in the graph arises from the operation necessary to add an edge. 
When a new connection is established between two vertices, resulting shadow labels must be computed.
To do so, interpolation between the two associated joint configurations is utilized to obtain a number of evenly spaced poses in $\mathcal{C}^N$. 
Shadow events are then computed at these evenly spaced joint configurations, propagating the intermediate labels between the vertices.

Upon adding a new edge, the algorithm recursively searches through the neighbours of the vertex, updating the dominated labels.
This acts as bookkeeping for a solutions.
If the reachable labels are all clear for a given vertex, the vertex must denote a full clearing of the environment.
Upon this condition being met, we may then reconstruct a solution from the intermediate waypoints between the root and the cleared node, as in any tree-based motion planning method.

The authors utilize three constraints to filter which edges should be added to the graph.
The first is mutual visibility - a line of sight, or obstacle free straight line path, must exist between each pursuers configuration at vertex $i$ and its corresponding configuration at vertex $i+1$.
The second is edge-length, with a maximum distance being set between two configurations.
Finally, a minimum cycle length is set to ensure that computation is not wasted on low-information configuration changes.

Numerous sampling strategies are explored, but none seem to outperform uniform sampling in the joint configuration space.
With the details outlined, the full algorithm is depicted in Algorithm \ref{}.


\subsection{Visibility Roadmaps}
In \cite{vis_roadmap}, an extension to SG-PEG is proposed. 
Several key innovations are detailed, including an improved visibility-based sampling distribution, a solution refinement method, and a process for iteratively increasing the number of pursuers until a solution can be provided.
Due to the references to visibility roadmaps in the paper title, we refer to this variant as visibility-roadmap SG-PEG~(VR-SG-PEG).
We note that, as we are interested in evaluating each detailed algorithm in sterile and identical conditions, we omit the process of increasing the number of pursuers from our method, instead keeping this fixed based on a given configuration.

In place of the uniform sampling recommended in SP-PEG, VR-SP-PEG uses an informed sampling method, referred to as web-sampling, to improve the density of samples in interesting regions.
By extension, this nominally improves convergence properties of the planner, at the cost of higher levels of computation.
The sampling proceeds in two phases: an initial visibility covering phase and an intersection sampling phase.

In the first phase, a set of initial points $\mathcal{P}\subset \mathcal{C}$ is constructed, referred to as a covering set.
This set is generated as follows: each initial point $p$ is sampled sequentially and randomly from outside the set of visible points in $\mathcal{C}$, i.e a sample $p_i$ is selected such that $p_i \notin \cup_{p_j\in \mathcal{P}}\mathcal{V}(p_j)$. This process continues until these mutually non-visible points cover the entire configuration space,$\cup_{p_j\in \mathcal{P}} \mathcal{V}(p_j) = \mathcal{C}$. 

In the second phase, a series of points, denoted by the set $\mathcal{Q}$, are sampled to expand the roadmap data structure.
This is done by sampling pairs of points $p_i, p_j \in \mathcal{P}$, denoted intersection points.
A point is then sampled uniformly from the intersection of the individual visibility cones of each point $\mathcal{V}(p_i)\cap \mathcal{V}(p_j)$, if the intersection is non-empty.
The so-called web is the union of the initial and intersection points $\mathcal{W} = \mathcal{P}\cup \mathcal{Q}$.
A separate web is sampled for each pursuer, and if a web is ever exhausted, a new set of webs is generated to continue.
The pursuit-evasion graph is constructed by sampling points from these webs without replacement.


The second innovation of note is the inclusion of a solution refinement step, devised to reduce unnecessary movement of the robots.
This acts as a post-processing step, filtering out the extraneous plan branches.
Iteratively, two non-adjacent points from the solution $z_a, z_b$ are selected to check if a shortcut from $z_a$ to $z_b$ is still a valid solution.
In addition to standard kinematic and collision avoidance constraints, the algorithm checks whether adjusting the solution in this manner clears the same set of shadows as the original solution, using the procedure laid out in Subsection \ref{subsec:peg}.

\subsection{ViPER}

ViPER is the learning-based algorithm included in our comparison.
It represents the known free space as a graph $G_t=(V_t,E_t)$ of candidate viewpoints and traversable edges.
At every decision step, each pursuer observes an augmented version of this graph containing relative node positions, teammate occupancy, frontier utility, uncovered-frontier utility, cleared-state indicators, and an $A^*$ guide signal.
The shared policy $\pi_\theta(a_i(t)\mid o_i(t))$ then chooses a neighboring viewpoint for each pursuer, so the learned action space remains tied to feasible motion on the map.

The map is divided into occupied cells $\mathcal{M}_o$, free cells $\mathcal{M}_f$, and cleared cells $\mathcal{M}_c$; uncovered frontiers between $\mathcal{M}_c$ and $\mathcal{M}_f\setminus\mathcal{M}_c$ are the locations through which a worst-case evader can recontaminate cleared space.
ViPER optimizes synchronized team motion, where the cost of a step is the longest distance traveled by any pursuer before the next decision.
Its shared reward is
\[
\begin{aligned}
r_t =
c_1\left(|\mathcal{M}_{c,t+1}|-|\mathcal{M}_{c,t}|\right)
-c_2 \max_i \|\psi_i(t+1)-\psi_i(t)\|\\
{}+
\mathbf{1}_{\mathcal{M}_c=\mathcal{M}_f^*}r_f .
\end{aligned}
\]
The first term rewards net clearing, the second penalizes team travel, and the final term rewards full task completion.

The network uses graph attention to encode the current viewpoint graph and a decoder that scores only feasible neighboring nodes.
Training uses Soft Actor-Critic~\cite{haarnoja2018soft} under CTDE: the actor receives the decentralized graph observation, while the critic is given privileged map and team-action information.
During evaluation, only the actor is used.
In our implementation, ViPER is treated as an online planner: we construct the visibility graph, compute node features from the shared map, query the actor for each pursuer, execute the selected moves, and evaluate the resulting trajectory with the same shadow-tracking and tournament metrics used for the other methods.

\section{Comparison Methodology}\label{sec:comp}

\section{Numerical Results}\label{sec:results}

\begin{table*}[t]
	\centering
	\caption{Comparison of Planning Algorithms Across Different Maps}
	\label{tab:comparison}
	\renewcommand{\arraystretch}{1.3}
	\setlength{\tabcolsep}{5pt}
	
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		
		\multirow{2}{*}{\textbf{Map}} & \multirow{2}{*}{\textbf{Algorithm}} 
		& \multicolumn{2}{c|}{\textbf{Time (s)}} 
		& \multirow{2}{*}{\textbf{Coverage (\%)}} 
		& \multirow{2}{*}{\textbf{Success Rate (\%)}} 
		& \multicolumn{2}{c|}{\textbf{Path Length}} \\
		\cline{3-4} \cline{7-8}
		
		& 
		& \textbf{Mean} & \textbf{Std} 
		& 
		& 
		& \textbf{Mean} & \textbf{Std} \\
		\hline
		
		% -------- Map 1 --------
		\multirow{4}{*}{\textbf{Map 1}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
		% -------- Map 2 --------
		\multirow{4}{*}{\textbf{Map 2}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
		% -------- Map 3 --------
		\multirow{4}{*}{\textbf{Map 3}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
		% -------- Map 4 --------
		\multirow{4}{*}{\textbf{Map 4}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
		% -------- Map 5 --------
		\multirow{4}{*}{\textbf{Map 5}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\centering
	\caption{Performance Comparison on Map X with Varying Number of Robots}
	\label{tab:scaling}
	\renewcommand{\arraystretch}{1.3}
	\setlength{\tabcolsep}{5pt}
	
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		
		\multirow{2}{*}{\textbf{\# Robots}} & \multirow{2}{*}{\textbf{Algorithm}} 
		& \multicolumn{2}{c|}{\textbf{Time (s)}} 
		& \multirow{2}{*}{\textbf{Coverage (\%)}} 
		& \multirow{2}{*}{\textbf{Success Rate (\%)}} 
		& \multicolumn{2}{c|}{\textbf{Path Length}} \\
		\cline{3-4} \cline{7-8}
		
		& 
		& \textbf{Mean} & \textbf{Std} 
		& 
		& 
		& \textbf{Mean} & \textbf{Std} \\
		\hline
		
		% -------- Robots = 1 --------
		\multirow{4}{*}{\textbf{1}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
		% -------- Robots = 2 --------
		\multirow{4}{*}{\textbf{2}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
		% -------- Robots = 5 --------
		\multirow{4}{*}{\textbf{5}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
		% -------- Robots = 10 --------
		\multirow{4}{*}{\textbf{10}}
		& \textbf{Alg 1} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 2} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 3} &  &  &  &  &  &  \\
		\cline{2-8}
		& \textbf{Alg 4} &  &  &  &  &  &  \\
		\hline
		
	\end{tabular}
\end{table*}

\section{Open Problems}\label{sec:open_prob}
% Based upon your work, what are some (specific) open problems in the topic area? Are there any major obstacles to progress (e.g. insufficient compute, unsolved theoretical issues)? Can you suggest possible ways to move forward?

\bibliographystyle{IEEEtran}
\bibliography{references}


\end{document}
